\documentclass[11pt
  , a4paper
  , article
  , oneside
%  , twoside
%  , draft
]{memoir}

\usepackage{control}
\usepackage[numbers]{natbib}
\usepackage[acronym,nomain]{glossaries}



\hypersetup{
  linkcolor  = {black}          % color of internal links
%  , citecolor  = {green}
%  , filecolor  = {magenta}
%  , urlcolor   = {cyan}
%  , unicode    = {true}
}
\makeglossaries

\begin{document}
\newcommand{\technumber}{
  RAON Control-Document Series\\
  Revision : v0.1,   Release : Nov, 19, 2014}
\title{\textbf{Requirements, Specification, and Interfaces \\ for the RAON Control System}}

\author{Jeong Han Lee\thanks{jhlee@ibs.re.kr} \\
  Control Team \\
  Rare Isotope Science Project\\
  Institute for Basic Science\\
  Daejeon, South Korea
}
\date{\today}

\renewcommand{\maketitlehooka}{\begin{flushright}\textsf{\technumber}\end{flushright}}
%\renewcommand{\maketitlehookb}{\centering\textsf{\subtitle}}
%\renewcommand{\maketitlehookc}{C}
%\renewcommand{\maketitlehookd}{D}

\maketitle

\begin{abstract}
This document is the Rare Isotope Science Project at Institute for Basics Science Requirements, Specification, and Interfaces for the RAON Accelerator Control System. It shows all general requirements and specifications for the RAON contron system. 
\end{abstract}

% Acronym definitions
\newacronym{epics}{EPICS}{Experimental Physics and Industrial Control System}
\newacronym{ract}{RACT}{RAON Accelerator Control Team}
\newacronym{vme}{VMEbus}{Versa Module Europa bus}
\newacronym{mvme}{MVME}{Motorola Single Board Computers}
\newacronym{ioc}{IOC}{Input Output Controller}
\newacronym{vdct}{VisualDCT}{Visual Database Configuration Tool}
\newacronym{opi}{OPI}{Operator Interface}
% Use the acronyms
%\gls{tc} is 3 hours behind \gls{adt} and 10 hours ahead of \gls{est}.
 
%Print the glossary
\printglossaries

\newpage
\chapter{Overview}
\label{overview}
The Control team has selected the \Gls{epics} \cite{EPICS3.14.12.3} as a main framework of the control system, because it is reliable, scalable, maintainable, low-cost system, and standard. The \Gls{epics} is an open-source, i.e. the source code is accessible, software that has various tools, libraries, and predefined applications developed by a world-wide user community and is used in large and small experimental physics projects such as particles accelerators, telescopes, and light sources since 1994. In addition, \Gls{epics} supports several hundred different modules with almost all bus types that produced by more than hundred manufacturers. One can find further information at \url{http:///www.aps.anl.gov/epics/}.

\begin{itemize}
  \item The \Gls{epics} clients shall be Debian Linux Stable PCs. The current version is Debian 7 Wheezy \cite{DEBIAN}. 
  \item \Gls{epics} servers on PC hardware shall run Debian Linux Stable (or other version as approved by \Gls{ract})
  \item \Gls{epics} servers on \Gls{vme} hardware shall run VxWorks version 6.9 (or other version as approved by \Gls{ract})
\end{itemize}


\chapter{EPICS Versions}
\begin{itemize}
  \item All \Gls{epics} software submitted by the Contractors, Collaborators, or any other third party shall be based on EPICS base version 3.14.12 (or later version as specified by \Gls{ract}.
  \item Where additional EPICS modules are used, the versions shall be according to Table~\ref{table:epicsmoduleversions}. Later versions may be specified by \Gls{ract}.
  \item If a module is not explicitly specified in Table~\ref{table:epicsmoduleversions}, the default version of this module used shall be the version provided in the synApps packages version 5.7. One can see the further information at \url{http://www.aps.anl.gov/bcda/synApps/}.
\end{itemize}



\begin{center}
\begin{longtable}[t]{>{\raggedleft\arraybackslash}p{2.4cm} |p{2cm}| p{8cm}}
\caption{EPICS Module Versions}
\label{table:epicsmoduleversions}\\
\toprule
\texttt{Name} & \textbf{Version} &  \textbf{comments}\\
\midrule
\endfirsthead
%%\multicolumn{4}{c}%
%%{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
\toprule
\texttt{Name} & \textbf{Version} &  \textbf{comments}\\
\midrule
\endhead
\midrule \multicolumn{3}{r}{\tablename\ \thetable\ -- \textit{Continued on next page}} \\
\bottomrule
\endfoot
\bottomrule
\endlastfoot
&\\
\texttt{asyn}         & R4-24 & \tiny \url{http://www.aps.anl.gov/epics/modules/soft/asyn/}\\
\texttt{stream}       & 2-6   & \tiny \url{http://epics.web.psi.ch/software/streamdevice/}\\
\texttt{ether\_ip}    & 2-26  & \tiny \url{http://sourceforge.net/projects/epics/files/ether_ip/}\\
\texttt{seq}          & 2.1.7 & \tiny \url{http://www-csr.bessy.de/control/SoftDist/sequencer} \\
\texttt{areaDetector} & R2-1  & \tiny \url{http://cars9.uchicago.edu/software/epics/areaDetector.html}\\
\texttt{motor}        & R6-8  & \tiny \url{http://www.aps.anl.gov/bcda/synApps/motor/}\\
&\\
\end{longtable}
\end{center}



\chapter{EPICS Support}
Where the contract involves the development of an \Gls{epics} interface to the equipment and any devices, the following itemized list shall apply.

\section{\Gls{ioc} platform}
\begin{itemize}
  \item The standard \Gls{ioc} hardware platform is an 1U rack mountable server.
  \item All \Gls{ioc} hardware shall be installed into the standard 19-in. rack by the Contractor.
  \item The \Gls{ioc} shall be included in the system performance tests at the Supplier's factory.
\end{itemize}


\section{Database development}
\begin{itemize}
  \item The Contractor shall provide \Gls{epics} databases with layout information compatible with the \Gls{vdct} \Gls{epics} database development tool \cite{vdct}.
\end{itemize}


\section{Device support}
\begin{itemize}
\item The Contractor shall supply \Gls{epics} device drivers and device support for any hardware delivered as part of this contract.
\item Where the Contractor provides a motion controller, the \Gls{epics} interface shall be the standard Moder record, or a set of records that provides equivalent functionality.
\end{itemize}

\section{\Gls{ract} Supplied Items}
\begin{itemize}
\item Debian Linux Stable, upon request.
\item Control System Studio, upon request.
\item A naming convention document for the control system.
\item A specification for the file structure to be used for software development. \textbf{Need to be a section in this document}
\end{itemize}

\section{\Gls{opi}}
Where the contract involves the development of an \Gls{epics} interface to the components, the following shall apply.
\begin{itemize}
\item The Contractor shall supply a GUI to perform the following functions:
  \begin{itemize}
  \item Equipment control panel(s) showing the state of all signals associated with the equipment. These should enable users to monitor and control the equipment for routine operation. It shall be possible to call up the engineering control panels from the Equipment control panel.
  \item The enginnering control panels should enable engineers to monitor and control all the available parameters of the equipment for commissioning and for troubleshooting.
  \end{itemize}
\item The \Gls{opi} shall be implemented in CSS/BOY.
\item The version of CSS used shall be the stable release, currently 3.3.11, or later version as approved by.
\item The version of BOY used shall be the stable release, currently 3.3.0, or later version as approved by .
\item The \Gls{opi} shall be implemented on a Linux PC. The version of Linux, defined in Chapter \ref{overview}, shall be used.
\item The \Gls{opi} for all optical elements shall include information about the direction and sign of the coordinate system used, including linar and rotations axes.

\end{itemize}

\section{Software Development}
\begin{itemize}
\item The Contractor shall provide current versions of all source code developed by the Contractor when the relevant Equipment is delivered to the Purchaser.
\item The Contractor shall provide final versions of all source code developed by the Contrator at the completion of equipment commissioning.
\item The Contractor shall provide software design documentation including functional specifications, sequence diagrams, class diagrams, and so on for the software developed to meet this contract.
\item A suitable level of commenting shall be adopted for all developed software. As an indication, comments should be provided, on average, for every subroutine and any complex code segment.
\item All software comments shall be in English or Korean. In case of Korean, UFT-8 encoding shall be used.
\item The Contractor shall allow the source code developed to meet this contract to be open source, consistent with the \Gls{epics} Open license.  
\end{itemize}

\section{Other Software}
\begin{itemize}
  \item The Contractor shall provide \Gls{epics} device support source code for all devices supplied as part of this contract.
\end{itemize}

\chapter{Acknowledgment}
The document is re-compiled by the author based on the original NSLS-II XFD RSI for the Controls and DAQ Systems \cite{LT-C-XFD-RSI-CO-001} in order to use it for the RAON accelerator control system. I owe much to Bob Dalesio and Wayne Lewis for fruitful discussions about the requirements, specifications, and interface for controls systems.


\clearpage
%\bibliographystyle{unsrt}
%\bibliographystyle{plainnat}
%\bibliographystyle{abbrvnat}
\bibliographystyle{unsrtnat}
%\bibliographystyle{ksfh_nat}
\bibliography{./refs}




\end{document}
